\documentclass[11pt, pdftex]{article}
\usepackage{epsf}
\usepackage{epsfig}
\usepackage{times}
\usepackage{ifthen}
\usepackage{comment}
\usepackage{amsmath, amsthm, amssymb}
\usepackage[margin=1in]{geometry}


\title{Deterministic Public Key Encryption}
\author{}
\date{}


\begin{document}
\maketitle

\section{Definitions}

\begin{enumerate}
\item Deterministic and Efficiently Searchable Encryption (BBO, Crypto 2007)
\begin{itemize}
\item Priv security ensures that a static adversary cannot generate side information about an underlying plaintext.  RO model construction.
\item requires high min-entropy in the plaintext space
\item ESE application and construction
\item CCA extension
\end{itemize}

\item Deterministic Encryption : Definitional Equivalences and Constructions without Random Oracles Relating the Security Notions (BeFiO, Crypto 2008)
\begin{itemize}
\item 7 security defs: (IND, 3 computational, 3 simulation based) against static adversaries.  All equivalent.  Standard model construction from TDP when plaintexts are UNIFORM/INDEPENDENT.  Extending this scheme requires stronger assumptions about the underlying TDP.
\item requires high min-entropy in the plaintext space
\item Build a randomized KEM from deterministic PK scheme
\end{itemize}


\item On notions of security for deterministic encryption, and efficient constructions without random oracles (BoFeO, Crypto 2008)
\begin{itemize}
\item PRIV-security for block sources, which assumes that for each message, the worst-case conditional min-entropy is at least some minimum value $t$
\item Equivalence to PRIV1 (and a single message IND notion).
\item Standard model constructions using ``lossy'' TDFs in both CPA and CCA settings
\item DDH-based and Pallier-based instantiations of the general construction, secure in the standard model.
\item KEM construction also provided
\end{itemize}

\item Hedged public-key encryption: How to protect against bad randomness (BBNRSSY, Asiacrypt 2009)
\begin{itemize}
\item IND-CDA security, where the joint distrib between the randomness and the message space has sufficiently high min-entropy
\item Assumes conditional min-entropy (like block sources) to achieve security
\item Adaptive source queries are allowed, but NOT after the PK has been revealed
\item Two RO constructions from IND-CPA schemes, two standard schemes from IND-CPA and PRIV schemes for block sources (using LTDFs)
\end{itemize}

\item Deterministic public-key encryption for adaptively chosen plaintext distributions (RSV, Eurocrypt 13)
\begin{itemize}
\item Adaptive security definition that generalizes across both IND-security and Hedged definitions
\item Adversary is GIVEN ACCESS to the public key and makes adaptive queries giving plaintext distributions rather than samples
\item Real-or-random game selects messages according to either the queried distribution (real) or uniform (random)
\item Two conditions on queries: each distribution has a min-entropy of $k$ (lower bounded) and the number of queried distributions are bounded by some polynomial w.r.t. the security parameter.
\item Build on the technique of BoFeO (using LTDFs) to yield a new standard model scheme that meets this adaptive definition.
\item CCA extension
\end{itemize}
\end{enumerate}

\section{Primitives}

\begin{enumerate}
\item Lossy Trapdoor Functions and Their Applications (PW, STOC 2008)
\begin{itemize}
\item New LTDF primitive requires that a TDF family be able to operate in two modes: lossy and injective
\item Security proven when both modes are indistinguishable
\item Instantiated under many assumptions (DDH applied later to D-PKE)
\end{itemize}

\item Instantiating Random Oracles via UCEs (BHK, CRYPTO 2013)
\begin{itemize}
\item Develops a notion of second-degree assumptions, which prove security against multi-stage adversaries
\item Capable of moving some random oracles into the standard model
\end{itemize}
\end{enumerate}

\section{Constructions}

\begin{enumerate}
\item Resisting Randomness Subversion : Fast Deterministic and Hedged Public-key Encryption in the Standard Model (BH, Eurocrypt 15)
\begin{itemize}
\item No new definitions.
\item Establishes the first standard model IND-secure D-PKE and H-PKE based on a combination of UCE for statistically uniform sources and LTDFs
\item Develop fast alternatives that yield KEM-DEM like efficiency
\item Generic U-PKE from D-PKE
\end{itemize}
\end{enumerate}


\section{Questions}
\begin{enumerate}
\item What is the hierarchy of syntax?  Can we express H-PKE as IV-PKE? 
\item Are there IV-PKE schemes that fall outside of H-PKE schemes?
\item Hedged definition: what's the use of picking two messages?
\item ACD security: how does limiting the number of distributions prohibit dependence?
\end{enumerate}

\end{document}